A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2024-11-19 manuscript/main.tex

@@

\subsubsection{RUD + AL (5 + 16 qubit)}
Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
For the 5 qubit, it is A2 HWE-CNOT

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/BSE/16qubit_BSE_MAE.png}
	\caption{16 qubit BSE MAE (kcal/mol)}
	\label{fig:16qubit_BSE_MAE}
\end{figure}

@@

\subsubsection{RUD + AL (5 + 16 qubit)}
Based off of the improvements shown in the function fitting dataset, we only used the best encoding ansatz pair for the real datasets
For the 5 qubit, it is  M-M-CZ HWE-CNOT

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{images/BSE/BSE5_RUDAL.png}
	\caption{5 qubit BSE MAE (kcal/mol) AL RUD}
	\label{fig:	BSE5_RUDAL}
\end{figure}

For 16 qubit A2 Hadamard
